implementation quality control

### 2018-02-27 analysis/analyses/4-method_characterisation/7_quality_control.Rmd

Table for the different checks
```{r, results="asis"}
library(kableExtra)
table <- checks %>% 
  mutate(
    weight = cell_spec(
      pritt("<span style='display: none;'>{aspect_id}</span> {weight}"), # add an invisible grouping indicator
      background = spec_color(weight, end=0.9,option="A",direction=-1),
      escape=FALSE,
      color="white"
    )
  ) %>%
  mutate(
    references = references %>% 
      gsub(",", "; ", .) %>% 
      {ifelse(!is.na(.), pritt("[{.}]"), "")} %>%
      {pritt("<span style='display: none;'>{aspect_id}</span> {.}")} # add an invisible grouping indicator
  ) %>% 
  select(aspect, weight, references, item, item_weight, !!qc_applications$application) %>% 
  mutate_at(vars(!!qc_applications$application), ~ifelse(., "✓", "")) %>% 
  rename_all(label_long) %>% 
  knitr::kable("html", escape=FALSE) %>% 
  kable_styling(bootstrap_options = "striped") %>% 
  collapse_rows(columns=1:3)

for (category in unique(checks$category)) {
  color <- qc_categories %>% filter(category == !!category) %>% pull(color)
  table <- table %>% 
    group_rows(
      label_long(category), 
      min(which(checks$category == category)), 
      max(which(checks$category == category)),
      label_row_css = pritt("background-color: {color}; color: #fff;")
  )
}

@@

cowplot::plot_grid(g1, g3, g2, ncol=2, nrow=2, labels = "auto") %>% 
  write_rds(figure_file("qc_over_time.rds"))
```

>>>>

Table for the different checks
```{r, results="asis"}
library(kableExtra)

invisible_grouper <- c(latex="\\iffalse {label_long(aspect_id)} \\fi {.}", html = "<span style='display: none;'>{aspect_id}</span> {.}")

citation_format <- c(
  latex=function(references) {
    if(is.na(references)) {
      ""
    } else {
      references %>% 
        gsub("@", "", .) %>% 
        str_split("[, \\n]+") %>% 
        first() %>% 
        glue::collapse(",") %>% 
        paste0("\\cite{", ., "}")
    }
  },
  html=function(references) {
    if(is.na(references)) {
      ""
    } else {
      references %>% 
        str_split("[, \\n]+") %>% 
        first() %>% 
        glue::collapse(";") %>% 
        {pritt("[{.}]")}
    }
  }
)

collapser <- c(latex="\\newline ", html="\n")

table <- map(c("latex", "html"), function(format) {
  table <- checks %>% 
    mutate(
      weight = cell_spec(
        weight %>% {pritt(invisible_grouper[[format]])}, # add an invisible grouping indicator
        format,
        background = spec_color(weight, end=0.9,option="A",direction=-1),
        escape=FALSE,
        color="white"
      )
    ) %>%
    mutate(
      references = map_chr(references, citation_format[[format]])
    ) %>% 
    select(aspect, weight, references, item, item_weight) %>% 
    rename_all(label_long) %>% 
    knitr::kable(format, escape=FALSE) %>% 
    kable_styling(bootstrap_options = "striped", latex_options = c("striped", "scale_down")) %>% 
    landscape() %>% 
    collapse_rows(1:3)
  # 
  # for (category in unique(checks$category)) {
  #   color <- qc_categories %>% filter(category == !!category) %>% pull(color)
  #   table <- table %>% 
  #     group_rows(
  #       label_long(category), 
  #       min(which(checks$category == category)), 
  #       max(which(checks$category == category)),
  #       label_row_css = pritt("background-color: {color}; color: #fff;")
  #   )
  # }

  table
}) %>% set_names(c("latex", "html"))

@@

cowplot::plot_grid(g1, g3, g2, ncol=2, nrow=2, labels = "auto") %>% 
  save_plot(figure_file("qc_over_time.svg"), ., base_width=10, base_height=10)
```
